Discrete Quantum Theories and Computing

### 2018-11-11 dissertation.tex
dissertation.tex Exported from dissertation.lyx

%% LyX 2.3.1-1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[11pt,twoside]{iuphd}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{fontspec}
\setmainfont[Mapping=tex-text]{Times New Roman}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\usepackage{verbatim}
\usepackage{booktabs}
\usepackage{mathrsfs}
\usepackage{enumitem}
\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage[all]{xy}

@@

A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections
of uncertain events \cites{Kolmogorov1950}{544199}{Griffiths2003}{Grabisch2016}.
Given a finite sample space~$\Omega$, and its power set $2^{\Omega}$
as the classical event space, a classical probability measure $\mu:2^{\Omega}\rightarrow\left[0,1\right]$
is a function subject to the following constraints: $\mu\left(\emptyset\right)=0$,
$\mu\left(\Omega\right)=1$, $\mu\left(\overline{E}\right)=1-\mu\left(E\right)$,
and $\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
for each pair of disjoint events $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$.

@@

\todo{Further discussion clean up until here.} Almost all QIVPMs
in Chapter~\ref{chap:QIVPM} are closely related to quantum probability
measures. For example, given a $\delta$-deterministic QIVPM, Lemma~\ref{lemma:delta2zero}
provides a way to derive a $0$-deterministic QIVPM $\barmuD:\events\rightarrow\left\{ \imposs,\necess\right\} $
which is essential a quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$
satisfying $\mu\left(P\right)$ is either $0$ or $1$. Moreover,
an interval map $f:\left[0,1\right]\rightarrow\mathscr{I}$ in Sec.~\ref{sec:Gleason}
provides an systemic way to derive QIVPMs from quantum probability
measures.

>>>>

%% LyX 2.3.1-1 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[11pt,twoside]{iuphd}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{fontspec}
\setmainfont[Mapping=tex-text]{Times New Roman}
\setcounter{secnumdepth}{3}
\setcounter{tocdepth}{3}
\usepackage{verbatim}
\usepackage{booktabs}
\usepackage{mathrsfs}
\usepackage{enumitem}
\usepackage{pdfpages}
\usepackage{graphicx}
\usepackage[all]{xy}

@@

A \emph{probability space} is a mathematical abstraction specifying
the necessary conditions for reasoning coherently about collections
of uncertain events \cites{Kolmogorov1950}{544199}{Griffiths2003}{Grabisch2016}.
Given a finite sample space~$\Omega$, and its power set $2^{\Omega}$
as the classical event space, a classical probability measure $\mu$
describe how likely every event~$E$ could happen by mapping $E$
to a number $\mu\left(E\right)\in\left[0,1\right]$.

is a function subject to the following constraints: $\mu\left(\emptyset\right)=0$,
$\mu\left(\Omega\right)=1$, $\mu\left(\overline{E}\right)=1-\mu\left(E\right)$,
and $\mu\left(E_{0}\cup E_{1}\right)=\mu\left(E_{0}\right)+\mu\left(E_{1}\right)$
for each pair of disjoint events $E_{0}\subseteq\Omega$ and $E_{1}\subseteq\Omega$.

@@

Almost all QIVPMs in Chapter~\ref{chap:QIVPM} are closely related
to quantum probability measures. For example, given a $\delta$-deterministic
QIVPM, Lemma~\ref{lemma:delta2zero} provides a way to derive a $0$-deterministic
QIVPM $\barmuD:\events\rightarrow\left\{ \imposs,\necess\right\} $
which is essential a quantum probability measure $\mu:\events\rightarrow\left[0,1\right]$
satisfying $\mu\left(P\right)$ is either $0$ or $1$. Moreover,
an interval map $f:\left[0,1\right]\rightarrow\mathscr{I}$ in Sec.~\ref{sec:Gleason}
provides an systemic way to derive QIVPMs from quantum probability
measures.
